Thermodynamic fragments in magic state theories

### 2020-12-01 appendix.tex
Tidying up of main text. Theory added yielding compact bounds on Phi+. Needs checking.

>>>>

\section{Theory on bounding the core functions}
The core function is $\Phi_+$ which is an even power cumulative function. We have good asymptotic bounds on the behaviour of the standard cumulative function $\Phi$, and the difference between these two functions is essentially given by the function
\begin{equation}
S(a,r,n) := \sum_{k=0}^r \binom{n}{k} (-a)^k.
\end{equation}
If we define the cumulative distribution function as
\begin{equation} 
\Phi(a,r,n) := \sum_{k=0}^r \binom{n}{k} a^k,
\end{equation}
then we have the simple relation
\begin{equation}
\Phi_+(a,r,n) = \frac{1}{2}( \Phi(a,r,n)  + S(a,r,n)).
\end{equation}
We would like some theory that estimates the value of this function for different parameter regimes. We can consider the function $f(x) = (1+x)^n$ and note that the function $S(a,r,n)$ is the $r$'th partial sum of this expansion at the point $x=-a$.

The truncated Taylor series tells us (e.g. see Wolfram MathWorld) that
\begin{equation}
f(x) = f(x_0) + (x-x_0) f'(x_0) + \dots \frac{(x-x_0)^r}{r!}f^{(r)}(x_0) + R_r(x)
\end{equation}
with a remainder term
\begin{align}
R_r (x)&= \int_{x_0}^x dt f^{(r+1)}(t) \frac{(x-t)^r}{r!} \\
&= \frac{(x-x_0)^{r+1}}{(r+1)!} f^{(r+1)}(x_*),
\end{align}
where in the second expression $x_* \in [x_0,x]$ is an implicit point that comes from the Mean Value Theorem.

Applying this to the function $f(x) = (1+x)^n$ with $x_0=0$ gives
\begin{equation}
(1+x)^n = \sum_{k=0}^r \binom{n}{k} x^k + R_r.
\end{equation}
Evaluating at $x=-a$ then gives us
\begin{equation}
S(a,r,n) = (1-a)^n - R_r(-a),
\end{equation}
where the key remainder term is given by
\begin{align}
R_r(-a) &= \int_0^{-a} dt f^{(r+1)}(t) \frac{(-a-t)^r}{r!} \\
&= \frac{(-a)^{r+1}}{(r+1)!} f^{(r+1)}(x_*).
\end{align}
We can also compute the derivative $f^{(r+1)}(x)$ explicitly, and get
\begin{equation}
f^{(r+1)}(x) = \frac{n!}{(n-r-1)!}(1+x)^{n-r-1}.
\end{equation}
Therefore, we have that
\begin{align}
R_r(-a) &= \frac{(-1)^r n!}{r!(n-r-1)!}\int_0^{-a} dt(1+t)^{n-r-1} (a+t)^r \\
&= \frac{(-a)^{r+1}}{r!} \binom{n}{r+1}(1+x_*)^{n-r-1},
\end{align}
where in the latter expression $x_* \in [-a,0]$. Also note that the first integral expression can be estimated via either Cauchy-Schwarz or the Hoelder inequality. Therefore, we can either work with an explicit form with an unknown (but bounded) parameter $x_*$, or we can use the integral form and provide concrete estimates on it value.

A very simple estimate, based on $x_*$ lying in the interval $[-a,0]$ gives
\begin{equation}
\frac{(-a)^{r+1}}{r!} \binom{n}{r+1} (1-a_*)^{n-r-1}\le R_r(-a) \le  \frac{(-a)^{r+1}}{r!} \binom{n}{r+1}.
\end{equation}

This in turn leads to the following bounds on $\Phi_+(a,r,n)$:
\begin{align}
\hspace{-2cm}2\Phi_+(a,r,n) &\le \Phi(a,r,n)+ (1-a)^n - \frac{(-a)^{r+1}}{r!} \binom{n}{r+1} (1-a)^{n-r-1} \nonumber \\
2\Phi_+(a,r,n) & \ge\Phi(a,r,n)+ (1-a)^n - \frac{(-a)^{r+1}}{r!} \binom{n}{r+1} .
\end{align}
Details need checking to see if I dropped any constants/signs. Are these bounds good in practice? Asymptotically?

### 2020-12-01 magic_paper.tex
Tidying up of main text. Theory added yielding compact bounds on Phi+. Needs checking.

\subsubsection*{Strange state distillation in the unital fragment}\label{sec:lcsu}

In this section we study the MSD process,
\begin{equation}\label{eq:sudist}
	\noisysn \xrightarrow{\E \in \O_{\id/3}} \noisys(\epsilon')\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{\mm},\ \nn = \tt + \mm,
\end{equation}
where we have uniformised the number of qutrits on both sides of the process.

In~\cref{app:lcsu_technical}, we define explicit expressions for the Lorenz curve of the $\NN$-copy, $\epsilon$-noisy Strange state in the unital fragment, 
\begin{equation}\label{eq:lcsu}
	\lc{\noisys(\epsilon')\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{\mm}}{\frac{1}{d}\id}(x),\ x\in[0,1].
\end{equation}
We call Lorenz curves of this type \emph{standard Lorenz curves}. \nick{expand (non-uniformity)}

@@

Here we focus on the part of the process described by the LHS of the Lorenz curves, in low noise regimes ($0 \leq \epsilon < 3/7$) with even numbers of initial and target copies.
In this case, the elbow expressions of the standard Lorenz curve in~\cref{eq:lcsu} are given by
\begin{align}
	x_i &= \Phi_+\left(2\ii;\NN,\frac{8}{9}\right), \\
	L_i &= \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_+\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right),
\end{align}
for $i=0,\dots,\frac{\NN}{2}$, where
\begin{equation}
	\Phi_+(\mmf; \nnf, p) \coloneqq \sum\limits_{\dummy=0}^{\mmf/2} \binom{\nnf}{2\dummy} p^{2\dummy} (1-p)^{\nnf-2\dummy}.
\end{equation}
Conventionally, we set $(x_{-1}, L_{-1}) = (0,0)$.

>>>>

\subsection{Strange state distillation in the unital fragment}\label{sec:lcsu}

We would now like to study the constraints coming soley from majorization in the unital fragment. We consider the problem of purifying $n$ copies of a noisy strange state $\rho(\epsilon)^{\otimes n}$ into a smaller number of $t$ copies of a less noisy strange state $\rho(\epsilon')^{\otimes t}$, with $\epsilon' \le \epsilon$. Since the state $\frac{1}{3} \I$ is  free state in this fragment the interconversion problem is unaffected if we tensor in copies of this maximally mixed state. This turns out to simply the Lorenz curve analysis, and so we focus on the process,
\begin{equation}\label{eq:sudist}
	\rho_S(\epsilon)^{\otimes 2n} \longrightarrow\sigma(\epsilon', n, t):=  \rho_S(\epsilon')^{\otimes 2t} \otimes \left( \frac{1}{3}\id \right)^{\otimes2n-2t}.
\end{equation}
Since the state on left-hand side of this of the form $\sigma(\epsilon, n, 0)$ it suffices to construct the Lorenz curve $L_\sigma(x)$ for the generic noisy strange state $\sigma(\epsilon, n ,t)$. For simplicity we assume that $\epsilon \le 3/7$, which is the threshold below which negativity is present in the state.

The state $\sigma(\epsilon, n, t)$ has the following Wigner quasi-distribution takes on values $w_k$, with associated multiplicities $m_k$ where
\begin{align}
w_k &=  \\
m_k &=
\end{align}
From this, it is readily seen that $L_\sigma(x)$ has elbows to the left-hand side of its peak located at points $x=x_i$ where
\begin{equation}
x_i = \Phi_+ (i, n , \frac{8}{9}),
\end{equation}
with $ i = 0,1, \dots , n$ and where $\Phi_+(i,n,p)$ is an even-power cumulant distribution function given by
\begin{equation}
\Phi_+( i, n,p) := \sum_{k=0}^{i} \binom{2n}{2k} p ^{2k} (1-p)^{2n-2k}.
\end{equation}
The value of the Lorenz curve at an elbow is given by
\begin{equation}
L_\sigma(x_i) \equiv L_i =  \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^{2n} \Phi_+\left(i;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right),
\end{equation}
and we define $(x_{-1}, L_{-1}) = (0,0)$.

In~\cref{app:lcsu_technical}, we define explicit expressions for the Lorenz curve of the $\NN$-copy, $\epsilon$-noisy Strange state in the unital fragment, 
\begin{equation}\label{eq:lcsu}
	\lc{\noisys(\epsilon')\too {\tt} \otimes \left( \frac{1}{3}\id \right)\too{\mm}}{\frac{1}{d}\id}(x),\ x\in[0,1].
\end{equation}

@@
